Wired for Success: Sweden's Electrical Innovators in the Age of Industrial Transformation

### 2023-10-30 index.qmd
add heatmaps

```{python}
import plotly.express as px
import numpy as np

# Generate random transition matrix
np.random.seed(42)
num_classes = 7
transition_matrix = np.random.randint(0, 100, (num_classes, num_classes))

# Define class labels
class_labels = [f"HISCLASS {i+1}" for i in range(num_classes)]

# Create heatmap
fig = px.imshow(
    transition_matrix,
    labels=dict(x="From", y="To", color="Count"),
    x=class_labels,
    y=class_labels,
    color_continuous_scale='Viridis',
    title="Transition Counts between HISCLASS"
)

# Show heatmap
fig.show()

>>>>

```{r}
knitr::include_url("assets/heatmap.html", height = "800")
